% !TeX root = ../thuthesis-example.tex

% 中英文摘要和关键字

\begin{abstract}
  精明的决策在妥善处理大流行病方面具有重要作用。为此，对人群进行全面和及时的诊断是必不可少的。不幸的是，2019年冠状病毒大流行(COVID-19)证明了在资源匮乏的地区缺乏有效、简便和便宜的诊断解决方案。
  
  本论文将介绍一种快速、敏感、价格实惠和冷链独立解决方案，该解决方案可在Low to Middle-Income Countries (LMICs)的临床样本中有效地检测出SARS-CoV-2。我们的技术被命名为CoronaDetective，可以以不到2美元的价格扩增SARS-CoV-2病毒基因组。CoronaDetective使用等温扩增技术，特别是Quenching of Unincorporated Amplification Signal Reporters in Reverse-Transcription Loop-Mediated Isothermal Amplification (QUASR-LAMP)，来扩增病毒RNA并发出荧光信号。此外，CoronaDetective已被证明对加纳和智利的许多临床样本有效。
  
  其次，我们设计并生产了两个开源硬件，一种是带有集成透射器水浴，另一种是实时LAMP机，主要目的是对放大效果进行定性和定量分析。这两个设备的设计均是开源的，很容易使用广泛的数字制造技术进行复制，便于在世界任何地方生产。事实证明，5美元的水浴与标准的实验室设备在孵化和分析反应方面的效果相同。尽管还有待进一步研究，但实时LAMP机显示了这种硬件的潜力，可以用50美元的成本进行定量分析。  
  
  我们希望，有了这些技术，在减少我们星球的诊断差距方面贡献自己的一份力。

  % 关键词用“英文逗号”分隔，输出时会自动处理为正确的分隔符
  \thusetup{
    keywords = {等温扩增 1, 开源硬件 2, 冠状病毒 3, 低资源诊断法 4, 节俭的科学 5},
  }
\end{abstract}
  .
\begin{abstract*}
Informed decision-making has a vital role in the proper management of pandemics. For this, a comprehensive and timely diagnosis of the population is essential. Unfortunately, the recent 2019 coronavirus pandemic (COVID-19) evidenced a lack of robust, simple and inexpensive diagnostic solutions that can be implemented in areas where resource scarcity becomes the bottleneck.
  
 This thesis will describe a fast, sensitive, affordable and cold-chain independent solution that allows robust detection of SARS-CoV-2 in clinical samples at Low to Middle-Income Countries (LMICs). Our technology starts with the CoronaDetective reactions, that allows the amplification of the SARS-CoV-2 viral genome by less than \$2. CoronaDetective uses isothermal amplification technologies, particularly Quenching of Unincorporated Amplification Signal Reporters in Reverse-Transcription Loop-Mediated Isothermal Amplification (QUASR-LAMP),  to amplify the viral RNA and generate a fluorescent signal. Furthermore, CoronaDetective has been proven to work with many clinical samples in Ghana and Chile.
  
Secondly, two open-source hardware devices, a water bath with an integrated transilluminator and a Real-Time LAMP machine, have been designed and produced with the primary goal of performing the qualitative and quantitative analysis of the amplification. The designs of both devices are open source and easy to replicate using widespread digital fabrication techniques, facilitating their production in any part of the world. The \$5 water bath has been proven to work equally to standard laboratory equipment for incubating and analyzing the reactions. Although more work is still needed, the Real-Time LAMP machine shows the potential of this hardware to perform the quantitative analysis at the cost of \$50. 
  
 We hope that, with these technologies, we add our little grain of sand in reducing the diagnosis gap in our planet.


  % Use comma as separator when inputting
  \thusetup{
    keywords* = {Isothermal amplification, Open-Source Hardware, Coronavirus, Low-Resources Diagnostics, Frugal science},
  }
\end{abstract*}
